---
title: "Assignment 1"
author: "Anuraag Vasal"
date: "10/22/2021"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
library(dplyr)  
library(readr)
Retailonline <- read.csv("Online_Retail.csv")
```
#The breakdown of the number of transactions by countries

```{r}
Retailonline_country  <- as.data.frame(table(Retailonline$Country))
Retailonline_country["Percentage"] <- Retailonline_country$Freq/NROW(Retailonline) * 100
names(Retailonline_country) <- c("Country","Count","Percentage")
Retailonline_country[Retailonline_country$Percentage > 1,]
```
#Countries accounting for more than 1% of the total transactions
EIRE,France,Germany and United Kingdom are the 4 countries that accounts for more than 1 % of total transactions.

#Adding new variable ‘TransactionValue’ which is the product of the exising ‘Quantity’ and ‘UnitPrice’ variables.
 
```{r}
Retailonline["TransactionValue"] <- Retailonline$Quantity * Retailonline$UnitPrice
head(Retailonline)
```
#Using the newly created variable, TransactionValue, showing the breakdown of transaction values by countries.
```{r}
Retailonline%>%group_by(Country)%>%summarise(Total=sum(TransactionValue))
Retailonline_transactionwise <- Retailonline%>%group_by(Country)%>%summarise(Total=sum(TransactionValue))
```
#Countries with total transaction exceeding 130,000 British Pound. 
```{r}
Retailonline_transactionwise[Retailonline_transactionwise$Total>130000,]
```
#Converting ‘InvoiceDate’ into a POSIXlt object

```{r}
Temp <- strptime(Retailonline $ InvoiceDate,format='%m/%d/%Y %H:%M',tz='GMT')
Retailonline$New_Invoice_Date <- as.Date(Temp)
Retailonline$New_Invoice_Date[20000]- Retailonline$New_Invoice_Date[10]
Retailonline$Invoice_Day_Week= weekdays(Retailonline$New_Invoice_Date)
Retailonline$New_Invoice_Hour = as.numeric(format(Temp, "%H"))
Retailonline$New_Invoice_Month = as.numeric(format(Temp, "%m"))
```
#Percentage of transactions (by numbers) by days of the week:

```{r}
Retailonline%>%group_by(Invoice_Day_Week)%>%summarise(count=n())%>%mutate(percentage=count/nrow(Retailonline)* 100) 
```
#The percentage of transactions (by transaction volume) by days of the week:

```{r}
Retailonline%>%group_by(Invoice_Day_Week)%>%summarise(Total=sum(TransactionValue))%>%mutate(percentage=Total/sum(Total)*100)
```

#The percentage of transactions (by transaction volume) by month of the year

```{r}
Retailonline%>%group_by(New_Invoice_Month)%>%summarise(Total=sum(TransactionValue))%>%mutate(percentage=Total/sum(Total)*100)

```

#The date with the highest number of transactions from Australia

```{r}
Retailonline%>%
filter(Country=="Australia")%>%
group_by(New_Invoice_Date)%>%
tally(sort = TRUE)%>%  
filter(n==max(n))
```
#The histogram of transaction values from Germany.
```{r}
Retailonline%>%
group_by(Country)%>%
filter(Country=="Germany")%>%
group_by(New_Invoice_Month)%>%
summarise(Total = sum(TransactionValue))-> Germany
hist(Germany$Total,main = "Transaction Values from Germany", xlab = "Total amount per Month", ylab = "Frequency")
```
#Customer having the highest number of transactions:
```{r}

Retailonline%>%
group_by(CustomerID)%>%
tally(sort = TRUE)%>%
filter(!is.na(CustomerID))%>%  
filter(n==max(n))
Retailonline%>%
group_by(CustomerID)%>%
summarise(Total=sum(TransactionValue))%>%
filter(!is.na(CustomerID))%>%  
filter(Total == max(Total))  
```
Customer with CustomerID 17841 has the highest number of transactions,and most valuable customer is CustomerID 14646 with spending of 279,489 Pounds.

#The percentage of missing values for each variable in the dataset:
```{r}
colMeans(is.na(Retailonline) *100)
```
Here , we can see that the missing values are present in the column of Customer ID and Description. The percentage of missing values in Customer ID column is 24.92669 % and for Description it is 0.2683107 %.

#The total number of transactions with missing CustomerID records by countries :
```{r}
NROW(Retailonline[is.na(Retailonline$CustomerID),])

```
The total number of rows in Customer ID column which have missing value is 135080

```{r}
Retailonline[is.na(Retailonline$CustomerID),] %>% group_by(Country) %>% summarise(count = n())
```
```{r}

Retailonline %>%
select(CustomerID,New_Invoice_Date)%>%
group_by(CustomerID)%>%
distinct(New_Invoice_Date)%>%
arrange(desc(CustomerID))%>%
mutate(DaysBetween = New_Invoice_Date - lag(New_Invoice_Date))-> Customerdaysbetweenvisit
Customerdaysbetweenvisit%>%
filter(!is.na(DaysBetween))-> Returningdaysbetweenvisits
mean(Returningdaysbetweenvisits$DaysBetween)
```
#The return rate of the goods purchased by customers from France:

```{r}
Retailonline_france_cancel <- Retailonline%>%filter(Country=="France",Quantity<0)%>%count
Retailonline_france_total <- Retailonline%>%filter(Country=="France")%>%count
Retailonline_ratio <- Retailonline_france_cancel$n / Retailonline_france_total$n
Retailonline_ratio * 100
```
The return rate for Customers of France is 1.741264 %

#The product that has generated the highest revenue for the retailer:

```{r}
Retailonline%>%group_by(Description)%>%summarise(Total=sum(TransactionValue))%>%arrange((desc(Total)))
```
Doctom Postage is the product that has generated the highest revenue for the retailer.

#Unique customers are represented in the dataset
```{r}
Retailonline_selectCustID <- Retailonline%>%select(CustomerID)%>%unique %>% nrow
Retailonline_selectCustID
```

The total number of unique customers in the dataset is 4373
